---
title: "TedTalks"
author: "Bryce Owen"
date: "4/6/2020"
output: html_document
---
```{r}
knitr::opts_chunk$set(echo = TRUE,message=FALSE, warning=FALSE)
```

```{r}
library(stringr)
library(tm)
library(wordcloud)
library(wesanderson)
library(ggplot2)
library(dplyr)
library(gridExtra)
library(readxl)
library(tidyr)
library(cluster)
library(forcats)
ted <- read_xlsx("/Users/Bryce/DataViz/TedTalks/TED Talks as of 3.29.2018.xlsx")
colnames(ted)
```

### Clean the Data
```{r}
clean.text <- function(x) {
    # to lowercase
    x <- tolower(x)
    # remove punctuation marks
    x <- gsub("[[:punct:]]", "", x)
    # remove numbers
    x <- gsub("[[:digit:]]", "", x)
    # remove tabs and extra spaces
    x <- gsub("[ |\t]{2,}", "", x)
    # remove blank spaces at the beginning
    x <- gsub("^ ", "", x)
    # remove blank spaces at the end
    x <- gsub(" $", "", x)
    # result
    return(x)
}
```

### View Number of Speakers by Number of TED Talks
```{r}
numtalks <- data.frame(table(ted$speaker_name))
table(numtalks$Freq)
```
2047 speakers have only done one TED Talk whereas one speaker has done a record nine TED Talks

### Get TED Talk Time in Minutes

```{r}
# Remove the 1899 Date from each duration entry
ted$duration <- gsub('1899-12-31 ', '', ted$duration)
# Create function to display talk time in minutes
ted$TalkTime <- sapply(strsplit(as.character(ted$duration), ":"), function(x) {
    x <- as.numeric(x)
    x[1] * 60 + x[2] + x[3]/60
})
```

### Establish Mean Time Talked in Frequency and Duration Table

```{r}
speakfreqandduration <- ted %>% group_by(speaker_name) %>% summarise(NumTalks = n(), 
    Mean.Talk.Time = mean(TalkTime, na.rm = TRUE)) %>% filter(NumTalks > 
    3)
# View talk time stats
summary(speakfreqandduration$Mean.Talk.Time)
```


### Interactive Table with Speakers, Number of Talks, and Mean Talk Time

```{r}

library(htmlwidgets)
suppressPackageStartupMessages(library(dplyr))
library(DT)# if (!require("DT")) install.packages('DT')
dt=datatable(speakfreqandduration, options=list(pageLength = 15), colnames = c('Speaker Name','Number of Talks','Average Talk Time (min)'))
dt
```


### Interactive Graph of Speakers Who Gave More Than 3 Talks

```{r, fig.height=10, fig.width=10}
library(taucharts)
library(plotly)

gg3 <- ggplot(na.omit(speakfreqandduration), aes(x = reorder(speaker_name, Mean.Talk.Time), 
    y = Mean.Talk.Time, fill = as.factor(NumTalks))) + geom_bar(stat = "identity") + 
    xlab("Speaker") + theme_bw() + theme(axis.text.y = element_text(size = 8), plot.title = element_text(hjust = 0.5), 
    axis.title.y = element_blank()) + coord_flip() + ggtitle("Speakers with more than 3 TED Talks") +guides(fill=guide_legend(title="Number of TED Talks Given")) + ylab("Mean Talk Time (Minutes)")

ggplotly(gg3)
```

### Get Top 20 Tags Using Wordmap Functions and Plot
```{r}
#Delineated with spaces instead of commas

TEDtags <- ted%>%select(tags)%>%separate(tags, c("tag1", "tag2", "tag3", "tag4", "tag5", "tag6", "tag7", "tag8", "tag9", "tag10","tag11", "tag12", "tag13", "tag14", "tag15", "tag16", "tag17", "tag18", "tag19", "tag20","tag21", "tag22", "tag23", "tag24", "tag25", "tag26", "tag27", "tag28", "tag29", "tag30","tag31", "tag32", "tag33", "tag34", "tag35", "tag36", "tag37", "tag38", "tag39", "tag40","tag41", "tag42", "tag43", "tag44", "tag45", "tag46", "tag47", "tag48", "tag49", "tag50"), sep = ",")%>% gather(tagnum, Tag, tag1:tag50)%>%filter(Tag != '')

#clean tags and remove beginning and end spaces

TEDtags$Tag<-trimws(TEDtags$Tag)
TEDtags$Tag<-tolower(TEDtags$Tag)


#get tag count and plot with tauchart

tagcount <-TEDtags%>%group_by(Tag)%>%summarise(Tag_count=length(Tag))%>%arrange(-Tag_count)

tagcount$Tag = fct_inorder(tagcount$Tag)

tauchart(tagcount[1:20,])%>%tau_bar('Tag_count','Tag',horizontal = TRUE)%>%tau_legend()%>%tau_tooltip()

```